draft_figures_12.18.18

### 2018-12-23 draft_figures_12.18.18.Rmd
regressions with larger categories and new MPA bar graphs with different data

@@

####Bar Chart: Coefficient Species Category

>>>>

##Larger Categories for ISSCAAP Codes
11,13 = freshwater fish = 1
22-24 = diadromous fishes = 2
31-35, 37 = marine fishes = 3
42-45,47 = crustaceans = 4
52-58 = molluscs = 5
74,76,77 = miscellaneous aquatic animals = 7

colnames(fisheries_recent_generousturf_1) <- c("Country", "assess_id_short", "Year", "CommName", "Biomass", "Catch", "BvBmsy", "FvFmsy", "Dbase", "SciName", "IdLevel", "SpeciesCat", "Profits", "MSY", "Price", "g", "k", "c", "phi", "itq", "ivq", "iq")

fisheries_recent_generousturf <- merge(turf_only, fisheries_recent_generousturf_1, by = c("Country", "SciName", "SpeciesCat"), all = "TRUE")

fisheries_recent_regression_1 <- fisheries_recent_generousturf %>%
  mutate(rightsbased = case_when(
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE | iq == FALSE | ivq == FALSE ~ "0"
    )) %>%
  mutate(MainCat = case_when(
    SpeciesCat == 11 | SpeciesCat == 13 ~ "1",
    SpeciesCat == 22 | SpeciesCat == 23 | SpeciesCat == 24 ~ "2",
    SpeciesCat == 31 | SpeciesCat == 32 | SpeciesCat == 33 | SpeciesCat == 34 | SpeciesCat     == 35 | SpeciesCat == 37 ~ "3",
    SpeciesCat == 42 | SpeciesCat == 43 | SpeciesCat == 44 | SpeciesCat == 45 | SpeciesCat      == 47 ~ "4",
    SpeciesCat == 52 | SpeciesCat == 53 | SpeciesCat ==54 |  SpeciesCat == 55 | SpeciesCat     == 56 | SpeciesCat == 57 | SpeciesCat == 58 ~ "5",
    SpeciesCat == 74 | SpeciesCat == 76 | SpeciesCat == 77 ~ "7"
  )) %>%
  select(Country, SciName, MainCat, rightsbased) %>%
  filter(MainCat != "NA")

merge_gdp_mc_rb <- merge(gdp, fisheries_recent_regression_1, by = c("Country"))

gdp_mc_rb <- filter(merge_gdp_mc_rb, MainCat != "NA" )

gdp_mc_rb$MainCat <- factor(gdp_mc_rb$MainCat)
gdp_mc_rb$rightsbased <- as.numeric(gdp_mc_rb$rightsbased)

itq_glm_mc <- glm(formula = rightsbased ~ gdp_center + MainCat, family = "binomial", data = gdp_mc_rb)

itq_glm_mc

summary(itq_glm_mc)

@@

##Larger Categories for ISSCAAP Codes
11,13 = freshwater fish = 1
22-24 = diadromous fishes = 2
31-35, 37 = marine fishes = 3
42-45,47 = crustaceans = 4
52-58 = molluscs = 5
74,76,77 = miscellaneous aquatic animals = 7

```{r}
fisheries_recent <- read_csv("data/fisheries_recent.csv")

fisheries_recent_turf_i_mc <- fisheries_recent_generousturf %>%
  mutate(rightsbased = case_when(
    turf == TRUE ~ "1",
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "0"
    ))%>%
  mutate(MainCat = case_when(
    SpeciesCat == 11 | SpeciesCat == 13 ~ "1",
    SpeciesCat == 22 | SpeciesCat == 23 | SpeciesCat == 24 ~ "2",
    SpeciesCat == 31 | SpeciesCat == 32 | SpeciesCat == 33 | SpeciesCat == 34 | SpeciesCat     == 35 | SpeciesCat == 37 ~ "3",
    SpeciesCat == 42 | SpeciesCat == 43 | SpeciesCat == 44 | SpeciesCat == 45 | SpeciesCat      == 47 ~ "4",
    SpeciesCat == 52 | SpeciesCat == 53 | SpeciesCat ==54 |  SpeciesCat == 55 | SpeciesCat     == 56 | SpeciesCat == 57 | SpeciesCat == 58 ~ "5",
    SpeciesCat == 74 | SpeciesCat == 76 | SpeciesCat == 77 ~ "7"
  )) %>%
  select(Country, SciName, MainCat, rightsbased) %>%
  filter(MainCat != "NA")

join_gdp_turf_i_mc <- merge(gdp, fisheries_recent_turf_i_mc, by = c("Country"))

gdp_turf_i_mc <- filter(join_gdp_turf_i_mc, MainCat != "NA" )

gdp_turf_i_mc$MainCat <- factor(gdp_turf_i_mc$MainCat)
gdp_turf_i_mc$rightsbased <- as.numeric(gdp_turf_i_mc$rightsbased)

turf_itq_mc_glm <- glm(formula = rightsbased ~ gdp_center + MainCat, family = "binomial", data = gdp_turf_i_mc)
turf_itq_mc_glm

summary(turf_itq_mc_glm)
```

###MPA New Costello Data
These MPAs are at least partitally no-take but some of the percentages are very low

mpa_costello_data <- read_excel("data/mpa_costello_data.xlsx")

##Choose only MPAs that have some no take
mpa_no_take <- mpa_costello_data %>%
  filter(no_take == "1")

mpa_no_take_10 <- top_n(mpa_no_take, 10, mpa_area)
mpa_no_take_10

##all countries
mpa_no_take_10$Country <- factor(mpa_no_take_10$Country, levels = mpa_no_take_10$Country[order(mpa_no_take_10$mpa_area)])

ggplot(mpa_no_take_10, aes(x = Country, y = mpa_area)) +
  geom_bar(stat = "identity")+
  ggtitle("Top 10 Countries with No Take MPAs")+
  coord_flip()+
  theme_bw()+
  ylab("Area km2")

These are the countries with the highest area of no-take
```{r}
mpa_costello_data <- read_excel("data/mpa_costello_data.xlsx")

##Choose only MPAs that have some no take
mpa_no_take <- mpa_costello_data %>%
  filter(no_take == "1")

mpa_no_take_area_10 <- top_n(mpa_no_take, 10, no_take_area)
mpa_no_take_area_10

##all countries
mpa_no_take_area_10$Country <- factor(mpa_no_take_area_10$Country, levels = mpa_no_take_area_10$Country[order(mpa_no_take_area_10$no_take_area)])

ggplot(mpa_no_take_area_10, aes(x = Country, y = no_take_area)) +
  geom_bar(stat = "identity")+
  ggtitle("Top 10 Countries with Largest No Take Areas")+
  coord_flip()+
  theme_bw()+
  ylab("Area km2")
